clusters

### 2015-07-23 cluster.rmd
starting knn app

@@

inv.knn<- function(df= all7d, predict= 'inv.mlsto', new.cases= c(1000), k=3){
        inv.knn = knn(df[,predict], df[new.cases,predict],
                df$pc.pro, k=k)
        indices<- attr(inv.knn,  "nn.index")
        #checkout the nearest neigbours!
        df %>% slice(c(new.cases, indices[1,])) %>% return

@@

#NA values don't work in knn function so turn all NA into zeroes
knn.binary[is.na(knn.binary)]<- 0
knn.binary$pc.pro<- all7d$pc.pro

@@

cat.knn<- function(df= all7d, predict= 'inv.mlsto', new.cases= c(1000), k=3, result.df= all7d){
        inv.knn = knn(df[,predict], df[new.cases,predict],
                df$pc.pro, k=k)
        indices<- attr(inv.knn,  "nn.index")
        dists<- attr(inv.knn, 'nn.dist') %>% t %>% as.data.frame %>% round(2)
        #checkout the nearest neigbours!
        final = cbind(result.df %>% slice(c(indices[1,])), dists)
        colnames(final)[names(final) %in% 'V1']<-'knn.dist'
        return(final)

b<- cat.knn(df= knn.binary, predict= colnames(knn.binary), new.cases= 60, k=5, result.df= all7d)

@@

```{r combine_knn, echo=FALSE}

b<- cat.knn(df= knn.binary, predict= colnames(knn.binary), new.cases= 60, k=20, result.df= all7d)
c<- inv.knn(df= b, predict= 'inv.mlsto', new.cases= 1, k=4) %>% slice(-1)
c

>>>>

write.csv(all7d,'all7d.csv')

@@

inv.knn<- function(df= all7d, predict= 'inv.mlsto', new.cases= c(1000), k=3){
        invo.knn = knn(df[,predict], df[new.cases,predict],
                df$pc.pro, k=k)
        indices<- attr(invo.knn,  "nn.index")
        #checkout the nearest neigbours!
        df %>% slice(c(new.cases, indices[1,])) %>% return

@@

#NA values don't work in knn function so turn all NA into zeroes
knn.binary[is.na(knn.binary)]<- 0
knn.binary$pc.pro<- all7d$pc.pro
knn.binary$mlsto<- all7d$mlsto

@@

cat.knn<- function(df= all7d, nn.by= 'inv.mlsto', predict='pc.pro', case= c(1000), k=3, result.df= all7d){
        invo.knn = knn(df[,nn.by], df[case,nn.by],
                df[,predict], k=k)
        indices= attr(invo.knn,  "nn.index")
        dists= attr(invo.knn, 'nn.dist') %>% t %>% as.data.frame %>% round(2)
        #checkout the nearest neigbours!
        final = cbind(result.df %>% slice(c(indices[1,])), dists)
        colnames(final)[names(final) %in% 'V1']<-'knn.dist'

        #final actions
        assign('index', indices, envir=.GlobalEnv)
        return(final)
}

bin<- knn.binary %>% select(-mlsto)
b<- cat.knn(df= bin, nn.by= colnames(bin)[-length(colnames(bin))], predict = 'pc.pro', case= 60, k=5, result.df= all7d)

@@

```{r combine_knn, echo=FALSE}
bin<- knn.binary %>% select(-mlsto)
b<- cat.knn(df= bin, nn.by= colnames(bin)[!grepl('pc.pro', colnames(bin))], predict = 'pc.pro', case= 80, k=10, result.df= all7d)
c<- inv.knn(df= b, predict= 'inv.mlsto', new.cases= 1, k=5) %>% slice(-1)
c
 #step 2 for user - option to sort by code.client?
d<- b[b[,'code.contact'] %in% b[,'code.contact'][1], ]
d
e<- inv.knn(df= d, predict= 'inv.mlsto', new.cases= 1, k=5) %>% slice(-1)
e
